TacticToe: Learning to Prove with Tactics

### 2018-09-03 tactictoe_jv.tex
JU tweaks in reproducibility

\paragraph{Reproducibility}
The \tactictoe project is part of the \holfour distribution 
which can be downloaded at \url{https://github.com/HOL-Theorem-Prover/HOL}.
\tactictoe modules can be found in the directory
\url{HOL/src/tactictoe}. The \url{README} file explains how to launch the 
recording 
process (which includes learning techniques such as orthogonalization),
use \tactictoe interactively and run a re-proving experiments on a theory. The 
recording process takes less than eight hours. An upper bound for 
the time necessary for the final experiment can be given by the formula:
\[\mathit{number\ of\ theorems} \times \mathit{timeout} = 7164 \times 60\ 
\mathit{seconds} = 
4.975\ \mathit{days}\] which translate in practice
to about $2.5\ \mathit{days}$ because successful searches stop before reaching 
the timeout. And finally, by running this experiment on 20 cores, we cut down 
the actual total time requirement to a few hours.

>>>>

\paragraph{Reproducibility}
The \tactictoe project is a part of the \holfour distribution 
which can be downloaded at \url{https://github.com/HOL-Theorem-Prover/HOL}.
The \tactictoe modules can be found in the directory
\url{HOL/src/tactictoe}. The \url{README} file explains how to launch the 
recording 
process (which includes learning techniques such as orthogonalization),
use \tactictoe interactively and run re-proving experiments on a theory. The 
recording process takes less than eight hours for the \holfour standard library. An upper bound for 
the time necessary for the final experiment can be given by the formula:
\[\mathit{number\ of\ theorems} \times \mathit{timeout} = 7164 \times 60\ 
\mathit{seconds} = 
4.975\ \mathit{days}\] 
This in practice translates 
to about $2.5\ \mathit{days}$, because successful searches stop before reaching 
the timeout. Finally, by running this experiment on 20 cores, we reduce
the actual wall clock time to several hours.
